%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Saikat Das} \\ \vspace{1pt}
    \small 83340 66167 $|$ \href{mailto:saikat.rog@gmail.com}{\underline{saikat.rog@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/thissaikat/}{\underline{linkedin.com/in/thissaikat}} $|$
    \href{https://github.com/saikat-rog}{\underline{github.com/saikat-rog}}
    \href{https://saikatdas.cloudfixmedia.com/}{\underline{https://saikatdas.cloudfixmedia.com}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Engineering and Management}{Kolkata, India}
      {Bachelor of Technology in Computer Science Engineering}{Aug. 2022 -- Present (Expected: 2026)}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      
    \resumeSubheading
      {Full Stack Developer}{June 2024 -- Present}
      {CloudFixMedia}{Kolkata}
      \resumeItemListStart
        \resumeItem{Implemented a client communication system, improving engagement and response times.}
        \resumeItem{Engineered a full-stack web application using React, Node.js, MongoDB, and Docker to create a seamless client interaction platform.}
      \resumeItemListEnd

    \resumeSubheading
      {DSA Instructor}{August 2023 -- July 2024}
      {Edzie}{Kolkata}
      \resumeItemListStart
        \resumeItem{Guided 2 batches of 20+ students in their DSA learning.}
        \resumeItem{Improved students' logic building and problem-solving skills.}
        \resumeItem{Explored diverse methods to mentor learners, leveraging the support of teaching assistants.}
        \resumeItem{Developed teamwork skills and gained in-depth knowledge of organizational management.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

  \resumeProjectHeading
        {\textbf{Hindsvaasthseva} $|$ \emph{React, Tailwind, REST API}}{December 2024 -- Present}
        \resumeItemListStart
          \resumeItem{Developed a platform for healthcare providers to manage patient data efficiently.}
          \resumeItem{Enabled users to access their medical history for improved diagnosis.}
          \resumeItem{Provided users with the convenience of booking appointments with nearby doctors.}
          \resumeItem{Implemented a feature for users to estimate treatment costs.}
        \resumeItemListEnd
  
       \resumeProjectHeading
        {\textbf{PuroTaja} $|$ \emph{Flutter with Get X and Dio, REST API, Git}}{November 2024 -- Present}
        \resumeItemListStart
          \resumeItem{Built a cross platform quick-commerce application that sells fish in multiple local areas .}
          \resumeItem{PuroTaja made it easy to focus on higher sales for a fish seller in few local areas.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{AttendMe} $|$ \emph{Flutter, Firebase Database, Dart based backend, Git}}{December 2023 -- February 2024}
        \resumeItemListStart
          \resumeItem{Developed an attendance management system accessible to both students and teachers.}
          \resumeItem{Designed a 'scan and attend' feature enabling quick attendance tracking using QR code scanning.}
          \resumeItem{Enhanced security by verifying location with GPS and controlling developer mode and system settings.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, Java, Dart, Python, MATLAB, JavaScript, TypeScript, HTML/CSS} \\
     \textbf{Frameworks}{: Flutter, React JS, Node.js, Express.js} \\ 
     \textbf{Database}{: MySQL, MongoDB, Firebase Firestore} \\ 
     \textbf{DevOps}{: Git and GitHub, Docker, Amazon Web Services} \\
     \textbf{Platforms}{: Linux, Windows}
    }}
 \end{itemize}

 %-----------CERTIFIED COURSES-----------
\section{Certifications}
  \resumeSubHeadingListStart
  \resumeSubheading
      {\href{https://www.hackerrank.com/certificates/dd8f41e196fa} {The Cybersecurity Threat Landscape}}{Linkedin Learning}{Jan 2024}{}
    \resumeSubheading
{\href{https://www.linkedin.com/learning/certificates/f1ad0fee7918badf79380b7ca9f8150092891eb43e30236ca0efa3602884c9bd?u=229219690}{Android Development Essential Training}}
      {Linkedin Learning}{Sep 2024}{}
      \resumeSubheading
      {\href{https://www.hackerrank.com/certificates/dd8f41e196fa} {Python}}{HackerRank}{March 2022}{}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
